---
title: "apa_acre"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Packages to be installed for spatial analysis
install.packages("tidyr")
install.packages("sp")
install.packages("spatial")
install.packages("rgdal")
install.packages("rgeos")
install.packages("raster")
install.packages("ggplot2")
install.packages("ggmap")
install.packages("spatstat")
install.packages("gstat")
install.packages("leaflet")
install.packages("maptools")
install.packages("magrittr")
install.packages("readr")
install.packages("lubridate")
install.packages("RColorBrewer")
install.packages("janitor")
install.packages("knitr")
install.packages("classInt")
install.packages("sf")


#load packages
```{r}

library(tidyr)
library(sp)
library(spatial)
library(rgdal)
library(rgeos)
library(raster)
library(ggplot2)
library(spatstat)
library(gstat)
library(leaflet)
library(maptools)
library(magrittr)
library(readr)
library(lubridate)
library(RColorBrewer)
library(janitor)
library(knitr)
library(classInt)
library(sf)

```
```{r}
#install.packages("sf")
library(sf)

#Create root based on OS
if(Sys.info()["sysname"] == "Windows"){
  team_path_ACRE <- "G:/"
} else {
  team_path_ACRE <- "/Volumes/GoogleDrive/"
}

#Create full file path
ACREs_path <- paste0(team_path_ACRE, "Shared Drives/Bren GP 2020 maricultura/Data/Raw_Data/shapefiles/APAs_ACREs")

#read the data
ACREs <- read_sf(dsn = ACREs_path, layer = "APAs_ACREs")
```

```{r read_shapefile}
##Create a SpatialPolygonsDataframe by reading in shapefile data
unzip("APAs_ACREs-2019004T182942z-001.zip")

```


```{r}
##Create a SpatialPolygonsDatafram by reading in shapefile data
apa_acre_shp <- readShapeSpatial("APAs_ACREs.shp",proj4string = CRS("+proj=longlat +datum=WGS854"))
```
```{r}
readOGR(dsn = "H:/shapefilepractice", layer = "APAs_ACREs.shp")
```
